MSD panels 1, 2 and 3 Explant Supernatant

### 2016-10-07 MSD_panels_1_2_3_explant_sup_analysis.Rmd
replaced missing values (below LOD) in LMF's data with miniumum conc for that analyte minus 10% so they would show up on the heat map.

```{r  merge and subtract mock, fig.width = 8, fig.height= 13, echo=FALSE}

@@

@@

This is just donors 317,318,323 and 324, which were interesting in the microarray

@@

@@

# 323-T2-Anything (i.e. no SD90 data)
# Didnt have sup for 326 T1 OR T2 (and this shows T3/T1 so we don't have anything)

@@

IL1a<-only_304_306 %>%
  filter(Assay == "IL1a")

@@

lessThanMinMIP1b<-min((na.omit(IL10$CalcConc)))-
  0.1 * (min((na.omit(IL10$CalcConc))))

@@

#remove some columns we don't need any more
#add a new "sample" column by pasting donor, timepoint, virus
no_missing_only_304_306<- no_missing_only_304_306 %>%
  select(-c(Sample,SampleName, avgECL))%>%
  mutate(Sample = paste(Donor,"-",Timepoint,"-",Virus, sep = ""))

@@

no_missing_only_304_306 <- no_missing_only_304_306 %>%
  mutate(avgEstConc = CalcConc * DilFactor) %>%
  select(-c(CalcConc, DilFactor))

@@

no_missing_only_304_306_numberInSets<-no_missing_only_304_306 %>%
         group_by(Donor,Timepoint,Assay)%>%
  select(Sample,Donor, Timepoint,Assay)%>%
  summarize(numInSet = n())

@@

mock_304_306 <- no_missing_only_304_306 %>%
  filter(Virus == "M")

@@

no_mock_304_306 <-
  no_missing_only_304_306 %>%
  filter(Virus !="M")

merge_304_306_mock<-merge(no_mock_304_306, mock_304_306, by = c("Donor", "Assay", "Timepoint"), all.x = TRUE, all.y = TRUE)

@@

#There is an NA where I have 304-T3-V1 but was dont have data for 304-T1-V1. This is ok, I know about this missing data. I will omit the row here.

merge24And3_304_306<-na.omit(merge24And3_304_306)

@@

@@

This is a heat map showing the same data as above, but fewer analytes and with Lamar's explant 304 and 306 data added in. The gray areas are there because we were missing some data from explant 304 because it was presumably below the LOD (i.e. no concentration was given in Lamar's spreadsheet).
```{r LMF_CL data log FC heatmap, echo=FALSE}

>>>>

```{r  merge and subtract mock, echo=FALSE}

@@

Note we did not have supernatents for:

Donor 323 for SD90, all time points

Donor 326 for SD90 and 186, 3hr and 8hr

@@

This is just donors 317,318,323 and 324, which were interesting in the microarray.

@@

Also note we were missing supernatents for:

Donor 323 for SD90, all time points

Donor 326 for SD90 and 186, 3hr and 8hr

@@

# 323-T1-V1, 323-T2-V1, 323-T3-V1 (so no SD90 data for any time point)
# Didnt have sup for 326 T1 OR T2 (and this shows T3/T1 so we don't have anything)

@@

IL1a<-only_304_306 %>%
  filter(Assay == "IL-1a")

@@

lessThanMinIL10<-min((na.omit(IL10$CalcConc)))-
  0.1 * (min((na.omit(IL10$CalcConc))))

@@

complete_304_306<-rbind(no_missing,missing)

#remove some columns we don't need any more
#add a new "sample" column by pasting donor, timepoint, virus
complete_304_306<- complete_304_306 %>%
  select(-c(Sample,SampleName, avgECL))%>%
  mutate(Sample = paste(Donor,"-",Timepoint,"-",Virus, sep = ""))

@@

complete_304_306 <- complete_304_306 %>%
  mutate(avgEstConc = CalcConc * DilFactor) %>%
  select(-c(CalcConc, DilFactor))

@@

complete_304_306_numberInSets<-complete_304_306 %>%
         group_by(Donor,Timepoint,Assay)%>%
  select(Sample,Donor, Timepoint,Assay)%>%
  summarize(numInSet = n())

@@

mock_304_306 <- complete_304_306 %>%
  filter(Virus == "M")

@@

no_mock_304_306 <-
  complete_304_306 %>%
  filter(Virus !="M")

merge_304_306_mock<-merge(complete_304_306, mock_304_306, by = c("Donor", "Assay", "Timepoint"), all.x = TRUE, all.y = TRUE)

@@

@@

#I want the scale to have max intensity a 10-fold change in either direction (log10(10)=1 on my scale and log10(0.1)= -1 on my scale) so I am going to set all values >=1 as 1 and all values <=-1 as -1. Right now there aren't any values >1 or <-1 but I'm doing this anyway since I did it for my data and want to have the same columns and protocol.

@@

This is a heat map showing the same data as above, but fewer analytes and with Lamar's explant 304 and 306 data added in.

Lamar's data did not have average concentrations for the following samples, probably becuse the electronic signal was below the level of detection:

MIP1b: 304-3hr-186

IL-1a: 304-3hr-186, 304-3hr-SD90, 304-3hr-Mock

IL-10: 304-3hr-Mock

In order to reflect on the heat map that these samples had low values, I set the average concentrations to 10% below the minimum  average concentration for the analyte of interest. I.e. I set the average concentration of MIP1b for sample 304-3hr-186 to 0.076, which is 10% less than the minimum MIP1b average concentration from among all the MIP1b samples where we *did* have data.

```{r LMF_CL data log FC heatmap, echo=FALSE}
